How much predator guts are required to predict trophic interactions?

### 2022-06-20 manuscript/ms_C2/ms_C2_v2.tex
Incorporated most comments from Guy, Eoin and David

\title{How much gut content data is required to predict trophic
interactions?}

\author{
    Anubhav Gupta
    \thanks{Corresponding author}
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:anubhav.gupta@ieu.uzh.ch}{\nolinkurl{anubhav.gupta@ieu.uzh.ch}}} \\
   \And
    Eoin O' Gorman
   \\
    School of Life Sciences \\
    University of Essex \\
  CO4 3SQ Colchester, UK \\
  \texttt{\href{mailto:e.ogorman@essex.ac.uk}{\nolinkurl{e.ogorman@essex.ac.uk}}} \\
   \And
    Other authors
   \\
    XXX XXX \\
    XXX XXX \\
  XXX XXX \\
  \texttt{XXX XXX} \\
   \And
    Owen L. Petchey
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:owen.petchey@ieu.uzh.ch}{\nolinkurl{owen.petchey@ieu.uzh.ch}}} \\
  }

@@

\usepackage{lineno}
\usepackage {amsmath}
\setlength\parindent{24pt}
\usepackage{setspace}\doublespacing
\begin{document}
\maketitle

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  One of the biggest obstacles in food web ecology is the time and
  effort required to adequately describe the structure of a food web
  using gut content data. Food web models such as the ADBM can be used
  to circumvent this problem by predicting the interactions based on
  easily measured characteristics, such as the size of organisms.
  However, presence-absence data such as gut content data is required to
  parameterise these food web models. And collecting and analysing these
  data from the field is an expensive and time consuming task.
  Therefore, it is crucial to know how much gut content data is required
  to parameterise food web models with high accuracy and high precision.
\item
  Here, we explore seven food webs in the literature and determine how
  much gut content data would be needed to accurately predict their
  structure using the ADBM. We use Bayesian computation to parameterise
  the ADBM, and true skill statistics to measure the goodness of fit,
  and do so while varying the amount of gut content data used in the
  parameterisation.
\item
  We estimated the minimum amount of gut content data required for seven
  different food webs that resulted in 95\% of the maximum true skill
  statistics achieved by the ADBM when all available gut content data
  was used. We found that incomplete gut content data can be used to
  parameterise the ADBM with the lowest amount of gut content data being
  28\% of the available gut content data.
\item
  These results suggest that one need not collect such a large quantity
  of gut content data to predict the structure of a food web, thereby
  reducing sampling effort considerably, while having little effect on
  precision or accuracy of predictions.
\end{enumerate}
\end{abstract}

\keywords{
    gut content data
   \and
    ADBM
   \and
    food web accuracy
   \and
    food web prediction
  }

@@

Knowledge about the trophic interactions in a food web is crucial in
ecology for purposes ranging from identifying keystone species (Jord'an
2009) to quantifying robustness of a food web to species extinctions
(Dunne, Williams, and Martinez 2002). This has led to the development of
numerous food web models (Allesina, Alonso, and Pascual 2008; Cohen,
Newman, and Steele 1985; Gravel et al. 2013; Petchey et al. 2008;
Tamaddoni-Nezhad et al. 2013). Along with inferring missing links in an
observed food web, the food web models are also used for ecological
forecasting (Hattab et al. 2016; Lindegren et al. 2010) and for
understanding the underlying mechanism governing the interactions in a
food web (Gorman et al. 2019).

Although food web models are constructed using prior theory about the
factors that determine trophic interactions, empirical data about
interactions is required to parameterise a model. For example, Petchey
et al. (2008) used presence-absence information about trophic
interactions to parameterise the allometric diet breadth model and
thereby predict species interactions. These empirical information about
interactions can come from diverse set of methods such as gut content
analysis (Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017),
stable isotope ratio analysis of tissues (Layman et al. 2007),
experimentation (Warren 1989), DNA metabarcoding of gut contents or
faeces (Roslin and Majaneva 2016) and literature research (Gray et al.
2015; Cohen and Mulder 2014a; Goldwasser and Roughgarden 1993a).

Each of these sources of information about trophic interactions has
shortcomings. For example: Stable isotope ratio analysis of the
organism's tissue does not give direct information of the diet of that
organism but rather gives approximate trophic position of that species
in the food web (Wada, Mizutani, and Minagawa 1991; Jennings and van der
Molen 2015). Although mixing models can be used to determine what prey
items are most likely fed upon by a predator, this results in
uncertainty in the estimates (Kadoya, Osada, and Takimoto 2012;
Crawford, Mcdonald, and Bearhop 2008). Similarly, DNA metabarcoding
could have issues in detecting secondary predation or cannibalism
(Pompanon et al. 2012; Nielsen et al. 2018) and is prone to
environmental contamination (e.g.~DNA in the water swallowed along with
DNA from an aquatic consumer's prey cannot be differentiated from actual
prey) (Kelly et al. 2014). Furthermore, construction of food webs via
literature review can lead to false positives--links included when in
reality no link would occur because it makes an assumption that the
species interactions inferred from a system will occur in another system
as well(Gray et al. 2015; Cohen and Mulder 2014b; Goldwasser and
Roughgarden 1993b).

Nielsen et al. (2018) have shown that gut content analysis method has a
better match with real diet when compared to other methods.

Acquiring food web data from gut content analysis is time consuming and
expensive (AG: Do we need a reference? Next sentence explains the
reason.). In part this is due to the perception that many gut contents
must be collected and analysed in order to be confident that the
majority of possible trophic links among species have been observed.
Furthermore, considerable time, resource investment, and expertise is
required to process the collected samples. Hence, there is of
considerable importance to know the minimum number of gut contents and
of which consumer species that are required to parameterise a food web
model with high accuracy and high precision, so that one knows when is a
good time to stop collecting any further empirical data on the food web.

Therefore, the key question we are interested in answering is how much
presence-absence information, in the form of gut content data, is
required to infer food web structure from a food web model with high
accuracy and high precision. In other words, how many samples of gut
content should one collect from the field to parameterise a food web
model? To answer this question, we use the presence-absence information
from gut content data to parameterise the allometric diet breadth model
(ADBM) thereby predicting trophic interactions in seven different food
webs using rejection approximate Bayesian computation, where the fit of
the model was measured using true skill statistics. We computed the true
skill statistics of the predicted food webs for different number of
predator guts to calculate the minimum number of gut content data to
infer food web structure. Our study provides a guideline on how many gut
content data is required to predict food web structure using a food web
model.

@@

In the upcoming sections, we present the empirical food webs, the
allometric diet breadth model (ADBM), and the gut content data used to
infer the trophic interactions. We also give a detailed account of using
partial gut content data to parameterise the ADBM using rejection
approximate Bayesian computation (ABC). We assessed model predictions
using the true skill statistic for comparison across food webs.

@@

In our study, we used food webs for which gut content data is available
at an individual level and data that is or that we could make FAIR
(Wilkinson et al. 2016). Presence and absence interactions of food web
data can be aggregated in different ways (Gilljam et al. 2011). A common
way of aggregating food web data is the taxonomic approach, in which
nodes in the food web are taxa (e.g.~species), or life stages of taxa,
and one species is said to feed on another species if at least one
individual of the latter is found in at least one gut of the former.
Another approach is based on size, rather than taxonomy, and in this the
nodes in the food web are size classes. Here, a feeding link occurs
between two size classes if at least one prey item within a size class
was found in the gut of another size class, irrespective of their
taxonomy.

In our study, we aggregate the gut content data on the basis of size
class because the food webs constructed using this approach were better
predicted by the ADBM compared to the taxonomic approach (Woodward et
al. 2010a), and this is because the ADBM is based on foraging rules
defined using the body sizes of organisms (Petchey et al. 2008).

Our study is based on the assumption that the food web constructed using
the complete gut content data is the true food web. However, this might
not be the case because the links are still under-sampled for many nodes
(Woodward et al. 2010b). This could result in a lower true skill
statistic (TSS) of the predicted food web from the ADBM, which can
result in a biased estimate of the minimum number of gut content data
required to achieve 95\% of the TSS achieved using complete gut content
data.

In the following sections 2.1.1-2.1.5, we briefly explain seven
empirical food webs used in our study. The text used in those sections
are paraphrased from Gilljam et al. (2011).

\hypertarget{broadstone-stream}{%
\subsubsection{Broadstone Stream}\label{broadstone-stream}}

Broadstone Stream (51\(^\circ\) 05' N 0\(^\circ\) 03' E; 120 m above
sea-level) is a second-order tributary of the River Medway in south-east
England. At the time of sampling in 1996--1997, the stream was acidic
(pH 4.7--6.6) and fishless. About 31 common species make up the
macroinvertebrate food web, including six major predators and
detritivores like stoneflies and chironomids (Woodward, Speirs, and
Hildrew 2005).

Between June 1996 and April 1997, thirty randomly scattered benthic
Surber sample-units (25cm \(\times\) 25cm quadrat; mesh aperture 330mm)
were taken every two months and kept in 5\% formalin. All individuals
retrieved from the benthos and identified in stomach contents had their
linear body dimensions quantified and converted to dry mass using known
regression formulae (listed in Woodward and Hildrew (2002)).

The predators' foreguts were dissected and analysed with 400
magnification in the Surber samples. The individual body masses of eaten
prey were calculated using the same methods as for the benthic samples,
using reference slides as a guide (Woodward, Speirs, and Hildrew 2005).
Over the six sample instances, a single dataset was produced. Each
predator and prey individual involved in a feeding relationship was
measured and converted into their respective body masses, resulting in a
total of 2893 individuals.

\hypertarget{celtic-sea}{%
\subsubsection{Celtic Sea}\label{celtic-sea}}

The Celtic Sea is a continental shelf area that is bounded by Ireland,
the United Kingdom, and the Bay of Biscay. Because the Barnes et al.
(2008) dataset, from which the data utilised in this chapter were taken,
did not provide precise sampling sites and dates, the data was pooled
throughout the whole time period and locations to capture broad
tendencies. Only places that were sampled consistently from 1987 to 2001
were used (Blanchard et al. 2005).

In a published global dataset of individual predator and prey body sizes
and taxonomy (Barnes et al., 2008), the feeding linkages of fish in the
Celtic Sea were described. The original stomach contents data were
acquired during annual surveys conducted by the Centre for Environment,
Fisheries, and Aquaculture Science (Cefas) on board research vessels
during dissections (Pinnegar et al. 2003). Barnes et al. (2008) used
known regression equations to measure predator and prey lengths and
convert them to body mass.

\hypertarget{afon-hirnant}{%
\subsubsection{Afon Hirnant}\label{afon-hirnant}}

Three sites in the Afon Hirnant, in North Wales, UK (\(52^\circ\) 52' N
\(03^\circ\) 34' W), were used for the study. The average yearly
discharge was 2.08 to 7.26 \(m^3/s\), with a pH ranging from 5.5 to 7.
(check Figueroa (2007) and Woodward et al. (2010c) for full details).
Invertebrates were collected using a Hess sampler (sampling area: 0.028
\(m^2\); mesh aperture 80 \(\mu m\)), with 15 sample-units obtained at
random at each site and season, totaling 180 samples across the sampling
period. The invertebrate fauna was promptly preserved in 100\% ethanol
and sorted in the lab. By removing predators' foreguts, which were
mounted in Euparal media and viewed at 400 magnification, feeding
interactions were determined.

Every predator's linear dimensions (for example, body length) and
individual prey items inside each predator's foregut were measured and
then translated to body mass values using published regression equations
for each taxon (presented in Woodward et al. (2010c)). If the prey items
were highly digested, the average body length of individuals in the same
family (Ephemeroptera, Plecoptera, or Trichoptera) in the habitat was
used. The body lengths of Chironomidae (Diptera) were calculated using
previously established species-specific regressions between head capsule
width and body length (Figueroa 2007).

\hypertarget{tadnoll-brook}{%
\subsubsection{Tadnoll Brook}\label{tadnoll-brook}}

The Tadnoll Brook is a tributary of the River Frome in Southern England,
UK, with a mean annual discharge of 0.35 \(m^3/s\) and a pH of 6.9--7.7.
(Edwards et al., 2009b).

A 240-m reach was sampled every two months between February and December
2005 to create the summary food web. A Surber sampler was used to
collect invertebrates every two months (0.06 m2; mesh aperture 300 mm).
20 random samples were taken on each occasion, stored in the field in
4\% (w/v) formalin, and then sorted for invertebrates. Fish were
captured with an electrofisher, anaesthetized with 2-phenoxyethanol,
recognised to species, measured, and weighed on each occasion (Woodward
et al., 2010). The guts of trout (Salmo trutta L.) with fork lengths
more than 70 mm were then flushed with a tiny manual water pump and
stored in 4\% formalin. For smaller trout and other fish species
(\emph{Cottus gobio}, \emph{Anguilla anguilla}, \emph{Phoxinus
phoxinus}, \emph{Barbatula barbatula}, \emph{Gasterosteus aculeatus}),
specimens were sacrificed and frozen for subsequent dissection.

Gut contents analysis was performed on each sample occasion for the fish
assemblage, whereas invertebrates had far less varied diets and were
only characterised in May and October. Individuals of the benthos'
numerically dominant or trophically important invertebrate taxa were
taken from the Surber samples, dissected, and the contents of the
foregut investigated for animal prey, which were recognised at
\(400\times\) magnification by comparison with reference specimens. The
taxa used to examine stomach contents covered more than 95\% of the
individuals observed in the Benthos. Wherever possible, predators' gut
contents were matched to species, and linear body dimensions were
measured. Using established regression equations, the dry mass of prey
items and invertebrate predators was calculated (Benke et al. 1999;
Ganihar 1997; Burgherr and Meyer 1997; Gonzalez, Basaguren, and Pozo
2002; Smock 1980; Edwards et al. 2009; MEYER 1989).

\hypertarget{guampoe-coilaco-and-trancura-rivers-chile}{%
\subsubsection{Guampoe, Coilaco and Trancura Rivers,
Chile}\label{guampoe-coilaco-and-trancura-rivers-chile}}

Three rivers (the Coilaco, Guampoe, and Trancura Rivers) in the
catchment area of the Tolten River in south Chile, South America, were
studied in a similar way. The Coilaco River (discharge 2.1--16.8
\(m^3/s\)), Guampoe River (output 1.8--7.5 \(m^3/s\)), and Trancura
River (discharge 8.8--49.3 \(m^3/s\)) are all pH 6.7--7.6 circumneutral
rivers (Figueroa 2007).

In each river, eight benthic samples were taken in each season between
1984 and 1985, totaling 96 sample-units for the whole sampling period
(Campos et al., 1985). Invertebrates were gathered using a Surber
sampler (sampling area: 0.09 \(m^2\); mesh aperture 250 \(\mu m\)) and
stored in 70\% ethanol before being transported to the lab for species
identification and food web analysis.

The feeding linkages were discovered by analysing the gut contents of
all individuals observed in each sample. Large invertebrates had their
guts removed and mounted in Euparal, whilst small specimens were mounted
whole and studied with \(400\times\) magnification. Following Schmid
(1993) and (Schmid-Araya et al. 2002), species prey items detected on
each gut were identified using previously mounted reference slides.
Using known regression equations (mentioned in Reiss and Schmid-Araya
(2008); Baumgärtner and Rothhaupt (2003); Miserendino (2001); Woodward
et al. (2010b)), all linear dimensions were translated to body mass
estimates.

@@

The allometric diet breadth model (ADBM) is based on optimal foraging
theory, specifically the contingency foraging model (MacArthur and
Pianka 1966). We chose this model for various reasons, including because
it uses the body size of organisms as input to predict feeding
interactions, and because of our familiarity with it. The ADBM predicts
the set of prey types (e.g.~species or sizes classes) a consumer should
feed upon to maximise its rate of energy intake (Petchey et al. 2008).
The foraging variables in the model are: energy content of the
resources, handling times of the prey, space clearance rate, and prey
densities. These are allometrically scaled to the body sizes of the
species. Further details on the foraging rules defined in the ADBM and
ADBM's predictive power across different food webs can be found in
Petchey et al. (2008).

@@

The accuracy of the predicted diet of the predators was measured using
true skill statistic (TSS) which takes into account the true and false
predictions of both the presence and absence of links defined as:

@@

\hypertarget{inferring-food-web-using-partial-gut-content-data}{%
\subsection{Inferring food web using partial gut content
data}\label{inferring-food-web-using-partial-gut-content-data}}

\textbf{Comment AG: Is it necessary to have the sections 1.1 and 1.2 of
the supplementary information in the Supplementary information or shall
the sections 1.1 and 1.2 be migrated to the main text (manuscript)?}

From an empirical dataset of gut content data, we take a random sample
of gut contents of specific size (see below) to create a partial gut
content dataset. We then fit the ADBM to this partial dataset.

@@

{\centering \includegraphics[width=500px]{../../manuscript/fig/ms_C2(1)}

@@

\caption{\label{fig:fig_ra} (a, c, e, g, i, k, m) Accuracy of the predicted food web measured using the true skill statistics, predicted by the ADBM parameterised using gut content data. Line and shaded grey region represents the mean and the prediction interval of 100 independent samples respectively. Red line represents the number of predator guts required to achieve a TSS of 95\% of the maximum TSS. (b, d, f, h, j, l, n) Ratio of the true skill statistic of the predicted food web by the ADBM parameterised using gut content data to that of the predicted food web constructed using gut content data only. The dashed line shows where the ratio is one for reference.}\label{fig:unnamed-chunk-1}
\end{figure}

To fit the ADBM to a gut content dataset (be it complete or partial), we
used the rejection ABC method we previously developed in Gupta, Furrer,
and Petchey (2022) to accept a parameter value from a prior distribution
which would have resulted in the minimum distance, where distance = 1 -
True skill statistic. The true skill statistic was computed between the
diets predicted from the ADBM, and those observed in the sampled gut
content data. We repeated this process \(n~(= 100)\) times for every
\(i\) number of guts, where \(i\) lies between 1 and total number of gut
content data in the pool.

@@

\begin{itemize}
\item
  Predators \(P: P = \{p_1, p_2, \dots, p_k \}\)
\item
  A pool of gut content data \(G: G = \{g_1, g_2, \dots, g_n\}\), where
  \(g_{n}\) is the observed diet matrix containing ones and zeros.
\item
  A model prediction
  \(model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}\),
  where \(d_{p_k}\) is the predicted diet matrix of predator \(k\)
  containing ones and zeros.
\item
  A summary statistic \(s(x): s(x) \subseteq model(\theta)\), where
  \(s(x)\) is the diet of some or all of the predators.
\item
  A distance function \(d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)\), which
  quantifies how close the observed diet is to the predicted diet of
  some or all of the predators.
\item
  An observed food web
  \(Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}\), where \(d_{p_k}'\)
  is the observed diet matrix of predator \(k\) containing ones and
  zeros.
\end{itemize}

@@

for \(i = 1, \dots, tgut\) where \(tgut\) is the total number of gut
content data in the pool \(G\)

@@

  \begin{itemize}
  \item
    Draw a set of gut content data \(y = \{g_1, g_2, \dots, g_i\}\) from
    the pool of gut content data \(G\)
  \item
    for \(k = 1, \dots, npar\) where \(npar\) is the number of parameter
    values to be sampled

>>>>

\title{How much predator guts are required to predict trophic
interactions?}

\author{
    Anubhav Gupta
    \thanks{Corresponding author}
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:anubhav.gupta@ieu.uzh.ch}{\nolinkurl{anubhav.gupta@ieu.uzh.ch}}} \\
   \And
    Eoin O' Gorman
   \\
    School of Life Sciences \\
    University of Essex \\
  CO4 3SQ Colchester, UK \\
  \texttt{\href{mailto:e.ogorman@essex.ac.uk}{\nolinkurl{e.ogorman@essex.ac.uk}}} \\
   \And
    Guy Woodward
   \\
    Georgina Mace Centre for the Living Planet, Department of Life
Sciences \\
    Imperial College London \\
  Ascot, Berkshire Sl5 7PY, UK \\
  \texttt{\href{mailto:guy.woodward@imperial.ac.uk}{\nolinkurl{guy.woodward@imperial.ac.uk}}} \\
   \And
    Other authors
   \\
    XXX XXX \\
    XXX XXX \\
  XXX XXX \\
  \texttt{XXX XXX} \\
   \And
    Owen L. Petchey
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:owen.petchey@ieu.uzh.ch}{\nolinkurl{owen.petchey@ieu.uzh.ch}}} \\
  }

@@

\usepackage{lineno}
\linenumbers
\usepackage {amsmath}
\setlength\parindent{24pt}
\usepackage{setspace}\doublespacing
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\begin{document}
\maketitle

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  One of the biggest obstacles in food web ecology is the time and
  effort required to adequately describe the structure of a food web
  using individual predator guts. Food web models such as the allometric
  diet breadth model (ADBM) can be used to circumvent this problem by
  predicting the interactions based on easily measured characteristics,
  such as the size of organisms. However, presence-absence data such as
  predator guts is required to parameterise these food web models, and
  collecting and analysing these data from the field is an expensive and
  time-consuming task. Therefore, it is crucial to know how much
  predator guts is required to parameterise food web models with high
  accuracy and high precision.
\item
  Here, we explore seven exceptionally well-characterised food webs in
  the literature and determine the minimum predator guts that would be
  needed to accurately predict their structure using the ADBM. We use
  Bayesian computation to parameterise the ADBM, and true skill
  statistics to measure the goodness of fit, and do so while varying the
  amount of predator guts used in the parameterisation to test the
  effect of sampling effort.
\item
  We found that incomplete predator guts can be used to parameterise the
  ADBM, with the lowest amount of predator guts being 28\% of the
  available predator guts.
\item
  These results suggest that one need not collect such a large quantity
  of predator guts to predict the structure of a food web, thereby
  reducing sampling effort considerably, while having little effect on
  precision or accuracy of predictions.
\end{enumerate}
\end{abstract}

\keywords{
    predator guts
   \and
    ADBM
   \and
    food web accuracy
   \and
    food web prediction
  }

@@

Knowledge about the trophic interactions in a food web is crucial in
ecology for purposes ranging from identifying keystone species (Jord'an
2009) to quantifying robustness of a food web to species extinctions
(Dunne, Williams, and Martinez 2002). This has led to the development of
numerous food web models and associated theory (Allesina, Alonso, and
Pascual 2008; Cohen, Newman, and Steele 1985; Gravel et al. 2013;
Petchey et al. 2008; Tamaddoni-Nezhad et al. 2013). Along with inferring
missing links in an observed food web, such food web models are also
increasingly used for ecological forecasting (Hattab et al. 2016;
Lindegren et al. 2010) and for understanding the underlying mechanism
governing trophic interactions in the wild (O'Gorman et al. 2019).

Although food web models are constructed using prior theory about the
factors that determine trophic interactions, empirical data about
interactions are required to parameterise a model. For example, Petchey
et al. (2008) and Gupta, Furrer, and Petchey (2022) used
presence-absence information about trophic interactions to parameterise
the allometric diet breadth model and thereby predict species
interactions. Such empirical information about interactions can come
from diverse set of methods such as gut content analysis
(Peralta-Maraver, Lopez-Rodriguez, and de Figueroa 2017), stable isotope
ratio analysis of tissues (Layman et al. 2007), experimentation (Warren
1989), DNA metabarcoding of gut contents or faeces (Roslin and Majaneva
2016) and literature research (Gray et al. 2015b; Cohen and Mulder
2014a; Goldwasser and Roughgarden 1993a) but each of these sources of
information about trophic interactions has serious shortcomings,
hindering the advancement of the field. For example: stable isotope
ratio analysis of the organism's tissue does not give direct
taxonomically resolved information of the diet of that organism, but
rather it provides approximate trophic position of that species in the
food web (Wada, Mizutani, and Minagawa 1991; Jennings and van der Molen
2015) and although mixing models can be used to determine what prey
items are most likely fed upon by a predator, this results in
uncertainty in the estimates (Kadoya, Osada, and Takimoto 2012;
Crawford, Mcdonald, and Bearhop 2008). Similarly, more recent approaches
using DNA metabarcoding may give much higher taxonomic resolution but
present other challenges, such as an inability to resolve secondary
predation or cannibalism (Pompanon et al. 2012; Nielsen et al. 2018)
which are common in nature and also being prone to environmental
contamination (e.g.~DNA in the water swallowed along with DNA from an
aquatic consumer's prey cannot be differentiated from actual prey)
(Kelly et al. 2014). Furthermore, construction of food webs via
literature review, which is one of the most common practices in food web
research, can lead to false positives--links included when in reality no
link would occur because it makes an assumption that the species
interactions inferred from a system will occur in another system as well
(Gray et al. 2015b; Cohen and Mulder 2014b; Goldwasser and Roughgarden
1993b). It is unsurpsing given the limitations of these proxy or
inferential approaches that authors such as Nielsen et al. (2018) have
shown that gut content analysis method has a better match with real diet
when compared to other methods.

Although gut content analysis is viewed as the ``gold standard'',
acquiring such food web data from direct gut content analysis is
extremely time consuming and expensive (Gray et al. 2015b) and it also
requires high skill levels in taxonomic identification, often involving
dissection and microscopy techniques (Hyslop 1980). The perception that
this is unavoidably laborious and costly is also in part due to the
assumption that many gut contents must be collected and analysed in
order to be confident that the majority of possible trophic links among
species have been observed. Most studies fail to quantify the effort
needed, with yield-effort curves being the exception rather than the
rule and those that have been done often point to the apparent need for
hundreds or thousands of guts to be analysed to fully capture a food
web's structure. Hence, it is of huge importance to know the minimum
number of predator guts required to parameterise a food web model with
high accuracy and high precision: this would enable researchers to
allocate resources more effectively a priori, and even having a rough
rule of thumb as to when is a good point to stop collecting any further
empirical data on the food web is far better than the current common
practice of simply taking a fixed set of samples with on yield-effort
analyses being undertaken.

Therefore, the key question we are interested in answering is how much
presence-absence information, in the form of predator guts, is required
to infer food web structure from a food web model with high accuracy and
high precision? In other words, how many samples of predator guts should
one collect from the field to parameterise a food web model? To answer
this question, we use different amount of predator guts to parameterise
the allometric diet breadth model (ADBM) thereby predicting trophic
interactions in seven different food webs using rejection approximate
Bayesian computation, and calculate the minimum number of predator guts
to infer food web structure. Our study provides a guideline on how many
predator guts are required to predict food web structure using a food
web model.

@@

We present the empirical food webs, the allometric diet breadth model
(ADBM), and the predator guts used to infer the trophic interactions. We
also give a detailed account of using partial predator guts to
parameterise the ADBM using rejection approximate Bayesian computation
(ABC). We assessed model predictions using the true skill statistic for
comparison across the food webs.

@@

In our study, we used food webs for which predator guts are available at
an individual level and data that is or that we could make FAIR
(Findable Accessible Interoperable Reusable; Wilkinson et al. (2016)).
In our study, first, we consider food webs where nodes are size classes
i.e.~individuals are aggregated into these size classes based on their
body size. A feeding link occurs between two size classes if at least
one prey item within a size class was found in the gut of another size
class of predator, irrespective of the taxonomy of the individuals. We
used this approach because of several reasons such as to take account
the ontogenetic shift in the diet of a predator (Woodward et al. 2010),
individual-based interaction based on body size which would not been
considered if nodes were aggregated based on taxonomy as a taxonomic
node can have a large variation in the body size. Food webs aggregated
using size can be used to model the impacts of commercial exploitation
on marine ecosystems (Jennings and Brander 2010). Second, we also
consider food webs where nodes are aggregated based on the taxonomy of
the individuals as this is the most common way of constructing food webs
in food web ecology.

Our study food webs are freshwater food webs except the Celtic Sea food
web which belongs to a marine ecosystem. Most of the food webs are
dominated by invertebrates except Celtic Sea which is dominated by
fishes and Tadnoll Brook which is dominated by fishes as well as
invertebrates. The food webs vary in the number of nodes, trophic links,
connectance and body sizes (Table 1).

Invertebrates in freshwater food webs were collected using Hess or
Surber sampler, whereas fishes were caught with electrofisher, and
anaesthetised using 2-phenoxyethanol in freshwater food webs. In case of
the Celtic Sea, trawling was used to catch fishes.

The foreguts of the collected invertebrate predators were dissected and
examined under the microscope. Regression equations were used to convert
predator and prey lengths to the respective body masses. In case if the
prey items were too highly digested for body lengths to be measured
reliably, previously established regressions based on head capsule width
were used as an alternative linear dimension. More detailed description
of these food webs is present in Gilljam et al. (2011).

\newgeometry{margin=1cm}
\begin{landscape}\begin{table}

\caption{\label{tab:unnamed-chunk-1}\label{fig:tab_1}Information about the empirical food webs. AG: Some information will be updated.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{8em}|l|l|l|l|>{\raggedright\arraybackslash}p{8em}|>{\raggedright\arraybackslash}p{8em}|>{\raggedright\arraybackslash}p{8em}}
\hline
Common food web name (Original Publication) & Location & Predation matrix source & Body size source & General ecosystem & Number of nodes & Number of links & Connectance & Body size range (mg) (approximate)\\
\hline
Broadstone Stream (Woodward
et al. 2010) & England, UK 51$^{\circ}$05'N 0$^{\circ}$03'E & Guy Woodward 2021 & Guy Woodward 2021 & Freshwater & 29 & 185 & 0.24 & $10^{-7}$ to $10^2$\\
\hline
Celtic Sea (Barnes et al. 2016) & British Isles and French coastal shelf 50$^{\circ}$50'N 08$^{\circ}$00'W & Barnes et al. 2016 & Barnes et al. 2016 & Marine & 48 & 386 & 0.17 & $10^{-2}$ to $10^4$\\
\hline
Tadnoll Brook & England, UK 50$^{\circ}$41'N 02$^{\circ}$19'W & NA & NA & Freshwater & 59 & 485 & 0.14 & $10^{-6}$ to $10^5$\\
\hline
Afon Hirnant (Woodward
et al. 2010) & Wales, UK, 50$^{\circ}$52'N 03$^{\circ}$34'E & David H. Figueora 2022a & David H. Figueora 2022a & Freshwater & 33 & 221 & 0.20 & $10^{-6}$ to $10^2$\\
\hline
Coilaco (Figueora 2007) & Chile 39$^{\circ}$17'S 71$^{\circ}$44'W & David H. Figueora 2022b & David H. Figueora 2022b & Freshwater & 45 & 123 & 0.06 & $10^{-6}$ to $10^2$\\
\hline
Guampoe (Figueora 2007) & Chile 39$^{\circ}$23'S 71$^{\circ}$410W & David H. Figueora 2022b & David H. Figueora 2022b & Freshwater & 44 & 139 & 0.07 & $10^{-6}$ to $10^3$\\
\hline
Trancura (Figueora 2007) & Chile 39$^{\circ}$26'S 71$^{\circ}$32'W & David H. Figueora 2022b & David H. Figueora 2022b & Freshwater & 35 & 78 & 0.06 & $10^{-6}$ to $10^1$\\
\hline
\end{tabular}}
\end{table}
\end{landscape}
\restoregeometry

@@

The allometric diet breadth model (ADBM) is based on optimal foraging
theory, specifically the contingency foraging model (MacArthur and
Pianka 1966). We chose this model because it can predict species
interactions based on an easily measurable trait body size. The ADBM
predicts the set of prey types (e.g.~species or sizes classes) a
consumer should feed upon to maximise its rate of energy intake (Petchey
et al. 2008). The foraging variables in the model are: energy content of
the resources, handling times of the prey, space clearance rate, and
prey densities. These are allometrically scaled to the body sizes of the
species. Further details on the foraging rules defined in the ADBM and
ADBM's predictive power across different food webs can be found in
Petchey et al. (2008).

@@

The accuracy of the predicted diet of the predators was measured using a
widely used accuracy measure in food web ecology namely true skill
statistic (TSS) (Gray et al. 2015b; Gravel et al. 2013; Gupta, Furrer,
and Petchey 2022). We chose this metric because it takes into account
the true and false predictions of both the presence and absence of links
defined as:

@@

\hypertarget{inferring-food-web-using-partial-predator-guts}{%
\subsection{Inferring food web using partial predator
guts}\label{inferring-food-web-using-partial-predator-guts}}

From an empirical dataset of predator guts, we take a random sample of
gut contents of specific size (see below) to create a partial predator
guts dataset. We then fit the ADBM to this partial dataset.

@@

{\centering \includegraphics[width=350px]{../../manuscript/fig/ms_C2_flowchart}

@@

\caption{\label{fig:fig_ra} Flowchart of the subsampling method implemented to predict the full food web from the food web model using the predator guts.}\label{fig:unnamed-chunk-2}
\end{figure}

To fit the ADBM to partial predator guts dataset, we used the rejection
approximate Bayesian computation method we previously developed in
Gupta, Furrer, and Petchey (2022) to accept a parameter value from a
prior distribution which would have resulted in the minimum distance,
where distance = 1 - TSS. The true skill statistic was computed between
the diets predicted from the ADBM, and those observed in the sampled
predator guts. We repeated this process \(n~(= 100)\) times for every
\(i\) number of guts, where \(i\) lies between 1 and total number of
predator guts in the pool.

@@

\begin{itemize}
\item
  Predators \(P: P = \{p_1, p_2, \dots, p_k \}\)
\item
  A pool of predator guts \(G: G = \{g_1, g_2, \dots, g_n\}\), where
  \(g_{n}\) is the observed diet matrix containing ones and zeros.
\item
  A model prediction
  \(model(\theta): ADBM(\theta) = \{d_{p_1}, d_{p_1}, \dots, d_{p_k}\}\),
  where \(d_{p_k}\) is the predicted diet matrix of predator \(k\)
  containing ones and zeros.
\item
  A summary statistic \(s(x): s(x) \subseteq model(\theta)\), where
  \(s(x)\) is the diet of some or all of the predators.
\item
  A distance function \(d(x_i, y) : d(x_i,y) = 1 - TSS(x_i, y)\), which
  quantifies how close the observed diet is to the predicted diet of
  some or all of the predators.
\item
  An observed food web
  \(Y: Y = \{d_{p_1}', d_{p_1}', \dots, d_{p_k}'\}\), where \(d_{p_k}'\)
  is the observed diet matrix of predator \(k\) containing ones and
  zeros.
\end{itemize}

@@

for \(i = 1, \dots, tgut\) where \(tgut\) is the total number of
predator guts in the pool \(G\)

@@

  \begin{itemize}
  \item
    Subsample a set of predator guts \(y = \{g_1, g_2, \dots, g_i\}\)
    from the pool of predator guts \(G\)
  \item
    for \(k = 1, \dots, npar\) where \(npar\) is the number of parameter
    values to be sampled
